\textsc{Taking Dyads Seriously}

### 2018-08-30 prezzy/netsMatter.tex
need a concl slide
minor edits and reshuffling

  \vspace{-10mm}
  Relational data consists of 
  \begin{itemize}
    \item - a set of units or nodes
    \item - a set of measurements, $y_{ij}$, specific to pairs of nodes $(i,j)$ 
  \end{itemize}

@@

@@

@@

The full AME framework enables us to not only account for the types of dependencies that often arise in dyadic data but also estimate them:

@@

\centering
\includegraphics[width=1\textwidth]{ameSimBias_all.pdf}

@@

\centering
\includegraphics[width=1\textwidth]{ameSimCover_all.pdf}

@@

\centering
\includegraphics[width=1\textwidth]{ameSimCorr.pdf}

@@

\footnotesize{
\begin{tabular}{lccccc}
	& Model &  Date Range & N. Actors  & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
	Reiter \& Stam (2003) & Logit &1945--1995 &  193 & Directed & Robust \\ 
	Weeks (2012) & Logit & 1946--1999 & 197 & Directed & Robust \\
	Gibler (2017) & Logit & 1816--2008 & 193 & Undirected & Robust \\ \bottomrule
\end{tabular}
}

@@

>>>>

  \vspace{-10mm}
  Much of international relations data consists of
  \begin{itemize}
    \item a set of units or nodes
    \item a set of measurements, $y_{ij}$, specific to pairs of nodes $(i,j)$ 
  \end{itemize}

  \centering
  \includegraphics[width=.5\textwidth]{dyadDF}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The approach that we will discuss here to deal with dependencies is the Additive and Multiplicative Effects (AME) model (Hoff 2015; Minhas, Hoff \& Ward 2018)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frame{
  \frametitle{Dependencies in relational data}

  \vspace{-10mm}
  To start to think about dependencies that arise in relational data ...
  \vspace{5mm}

@@

The full AME framework enables us to not only account for the types of dependencies that often arise in dyadic data but also estimate them in a fully Bayesian framework:

@@

\vspace{8mm}
\centering
\includegraphics[width=1\textwidth]{ameSimBias_all.pdf}

@@

\vspace{8mm}
\centering
\includegraphics[width=1\textwidth]{ameSimCover_all.pdf}

@@

\vspace{8mm}
\centering
\includegraphics[width=1\textwidth]{ameSimCorr.pdf}

@@

\vspace{5mm}
% \footnotesize{
% \begin{tabular}{lccccc}
% 	& Model &  Date Range & N. Actors  & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
% 	Reiter \& Stam (2003) & Logit &1945--1995 &  193 & Directed & Robust \\
% 	Weeks (2012) & Logit & 1946--1999 & 197 & Directed & Robust \\
% 	Gibler (2017) & Logit & 1816--2008 & 193 & Undirected & Robust \\ \bottomrule
% \end{tabular}
% }
\begin{tabular}{lcccc}
	& Model &  Date Range & N. Actors  & Dyads Type \\ \toprule
	Reiter \& Stam (2003) & Logit &1945--1995 &  193 & Directed \\ 
	Weeks (2012) & Logit & 1946--1999 & 197 & Directed \\
	Gibler (2017) & Logit & 1816--2008 & 193 & Undirected \\ \bottomrule
\end{tabular}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frame{
\frametitle{Next steps}

\begin{itemize}
	\item Dealing with time varying dependence structure
	\item Parsing out formation, persistence and dissolution
	\item Many other extensions (bipartite, endogenous multilayer networks, ...)
	\item Computational issues ... Bayesian models take time to converge 
\end{itemize}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
